### 2013-02-25 web/12.su.reg/exams/exam1.tex
Summer exam stuff.

\vfill
\centerline{\Large CS 2510 Exam 2 -- Summer 2012}

@@

Binary trees are one of the most widely used data structures in
computer science.  Here are three examples of binary trees of numbers:

\begin{verbatim}
         5        1           3
                   \         / \
                    2       4  18
                              /  \
                             9    12
                            /    /
                           7    3
\end{verbatim}

Nodes in a binary tree carry data, which in this case are numbers, and
a node has a left and right subtree.  Binary trees, like lists, may
contain \emph{any} number of elements, including 5, 8, 19, and 0.

\begin{enumerate}
\item Design a data definition for binary trees.  It must adequately
  represent any possible binary tree.

\item Give class diagrams corresponding to the data definition from
  part A.

\item Design a {\tt mirror} method that computes the mirror image of a
  binary tree.  For example, the mirror image of the above trees would
  be:

\begin{verbatim}
     5        1           3
             /           / \
            2           18  4
                       /  \
                     12    9
                       \    \
                        3    7
\end{verbatim}
\end{enumerate}

\end{problem}
\newpage
\ 
\end{document}

>>>>

\vfill
\centerline{\Large CS 2510 Exam 1 -- Summer 2012}

@@

A writing utensil may either be a pen or pencil.  A pen has a color
and an amount of ink, measured in microlitres (\(\mu\)l).  A pencil
has a graphite lead, measured in millimetres (mm).

Five microlitres of ink will write a line seven metres long, while a
graphite lead of 3 millimetres will write a line 22 metres long.

\begin{enumerate}
\item Design a data representation of writing utensils.

\item Give three examples of writing utensils.

\item Design a method for writing utensils that determines how long
  of a line it can write.
\end{enumerate}
\end{problem}
\newpage
\ 
\end{document}
